---
title: "assignment1"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
date: "2024-06-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- 
Dataset: https://www.kaggle.com/datasets/antfarol/car-sale-advertisements
install.packages(c("readr", "dplyr", "ggplot2")) 
-->


## Analysis


* Print the structure of your dataset
```{r}
library(readr)
car_ad <- read_csv("/Users/101501339/Documents/car_ad.csv")
str(car_ad)
```

* List the variables in your dataset
```{r}
names(car_ad)
```


* Print the top 15 rows of your dataset
```{r}
# List the variables in the dataset
head(car_ad, 15)
```


* Write a user defined function using any of the variables from the data set.
```{r}
# User-defined function to calculate average price
average_price <- function(data) {
  mean(data$price, na.rm = TRUE)
}

# Call the function
average_price(car_ad)
```


* Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset.
```{r}
# Load dplyr library
library(dplyr)

# Filter rows where price is greater than 10000
filtered_data <- car_ad %>%
  filter(price > 50000)

# Print the filtered data
head(filtered_data)
```


* Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset.
```{r}
# Select dependent and independent variables
reshaped_data <- car_ad %>%
  select(price, car, model, year, mileage)

# Print the reshaped data
head(reshaped_data)
```


* Remove missing values in your dataset.
```{r}
# Remove missing values
car_ad <- na.omit(car_ad)

# Print the cleaned data
head(car_ad)
```


* Identify and remove duplicated data in your dataset
```{r}
# Remove duplicated data
car_ad <- car_ad %>%
  distinct()

# Print the unique data
head(car_ad)
```

* Reorder multiple rows in descending order
```{r}
# Reorder rows in descending order by price
car_ad <- car_ad %>%
  arrange(desc(price), desc(year))

# Print the ordered data
head(car_ad)
```



* Rename some of the column names in your dataset
```{r}
# Rename columns
car_ad <- car_ad %>%
  rename(car_price = price, car_model = model)

# Print the renamed data
head(car_ad)
```

* Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame)
```{r}
car_ad <- car_ad %>%
  mutate(car_price_double = car_price * 2)

# Print the updated data frame
head(car_ad)
```

* Create a training set using random number generator engine.
```{r}
# Create a training set
set.seed(123)
training_indices <- sample(1:nrow(car_ad), 0.7 * nrow(car_ad))
car_ad <- car_ad[training_indices, ]

# Print the training set
head(car_ad)
```

* Print the summary statistics of your dataset
```{r}
summary(car_ad)
```

* Use any of the numerical variables from the dataset and perform the following statistical functions
```{r}
# Mean
mean_price <- mean(car_ad$car_price, na.rm = TRUE)

# Median
median_price <- median(car_ad$car_price, na.rm = TRUE)

# Mode
mode_price <- as.numeric(names(sort(table(car_ad$car_price), decreasing = TRUE))[1])

# Range
range_price <- range(car_ad$car_price, na.rm = TRUE)

# Print results
mean_price
median_price
mode_price
range_price
```

* Plot a scatter plot for any 2 variables in your dataset
```{r}
# Load ggplot2 library
library(ggplot2)
library(scales)
# Scatter plot of price vs mileage
ggplot(car_ad, aes(x = mileage, y = car_price)) +
  geom_point() +
  scale_y_continuous(labels = comma) +
  labs(title = "Price vs Mileage", x = "Mileage", y = "Price")
```

* Plot a bar plot for any 2 variables in your dataset
```{r}
# Bar plot of average price by make
ggplot(car_ad, aes(x = car, y = car_price)) +
  stat_summary(fun = mean, geom = "bar") +
  labs(title = "Average Price by Car", x = "Car", y = "Average Price") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

* Find the correlation between any 2 variables by applying Pearson correlation
```{r}
# Pearson correlation
correlation <- cor(car_ad$car_price, car_ad$mileage, method="pearson")

# Print correlation
correlation
```










